---
title: "ENAHO"
output: 
  html_notebook:
    number_sections: true
    toc: yes
  editor_options:
    markdown:
      canonical: false        
---

# ENAHO - Peru

La Encuesta Nacional de Hogares es la investigación que permite al Instituto Nacional de Estadística e Informática (INEI) desde el año 1995, efectuar el seguimiento de los indicadores sobre las condiciones de vida.

The National Household Survey is the research that allows the National Institute of Statistics and Informatics (INEI) since 1995, to monitor the indicators on living conditions.

**Source:**

-   [https://www.datosabiertos.gob.pe/dataset/encuesta-nacional-de-hogares-enaho-2020-instituto-nacional-de-estadística-e-informática-inei](https://www.datosabiertos.gob.pe/dataset/encuesta-nacional-de-hogares-enaho-2020-instituto-nacional-de-estadística-e-informática-inei){.uri}

-   <http://iinei.inei.gob.pe/microdatos/>

## Setup

```{r include=FALSE}
rm(list = ls())
```

```{r include=FALSE}
library(here)
```

```{r include=FALSE}
source("../../script/r/dataset/download_dataset.R")
```

## Dataset

```{r include=FALSE}
download_file("http://iinei.inei.gob.pe/iinei/srienaho/descarga/CSV/737-Modulo01.zip") # Household
download_file("http://iinei.inei.gob.pe/iinei/srienaho/descarga/CSV/737-Modulo02.zip") # People
download_file("http://iinei.inei.gob.pe/iinei/srienaho/descarga/CSV/737-Modulo03.zip") # Education
download_file("http://iinei.inei.gob.pe/iinei/srienaho/descarga/CSV/737-Modulo04.zip") # Health
download_file("http://iinei.inei.gob.pe/iinei/srienaho/descarga/CSV/737-Modulo05.zip") # Incomes
```




