---
title: "UBIGEO"
output: 
  html_notebook:
    number_sections: true
    toc: yes
  editor_options:
    markdown:
      canonical: false        
---

# UBIGEO

Ubigeo is the coding system for geographical locations (Spanish: Código Ubicacíon Geográfica) in Peru used by the National Statistics and Computing Institute (Spanish: Instituto Nacional de Estadística e Informática INEI[1]) to code the first-level administrative subdivision: regions (Spanish: regiones, singular: región), the second-level administrative subdivision: provinces (Spanish: provincias, singular: provincia) and the third-level administrative subdivision: districts (Spanish: distritos, singular: distrito). There are 1874 different ubigeos in Peru.

**Source:**

- https://en.wikipedia.org/wiki/UBIGEO
- https://www.datosabiertos.gob.pe/dataset/codigos-equivalentes-de-ubigeo-del-peru
- https://github.com/jmcastagnetto/ubigeo-peru-aumentado

## Setup

```{r include=FALSE}
rm(list = ls())
```

```{r include=FALSE}
library(dplyr)
library(stringr)
library(readr)

library(data.table)
library(here)
library(tictoc)
library(skimr)

library(fst)
```

```{r include=FALSE}
source("../../script/r/dataset/download_dataset.R")
```

### Ubigeo package

- https://github.com/jmcastagnetto/ubigeo

```{r}
library(ubigeo)
```


## Province

```{r}
ubigeo_province
```

## Department

```{r}
ubigeo_department
```
## District

```{r}
ubigeo_district
```

## CCPP (Centro Poblado)

```{r}
ubigeo_ccpp
```
